Profitability Prediction of Consulting Projects in the Construction Industry

### 2016-08-30 finalwriteup/draft.rmd

Consulting businesses give expert advice to other professionals in exchange for a fee based on the amount of time their consulting staff spends on the project. The deliverable 'expert advice' is generally in the form of a document or a package of documents. A document could range from a 5-page report written by a single person to a sequence of hundreds of drawings assembled by a team of 10 over many years. Despite the range of possible deliverables, before any project commences, the client and consultant must agree on a fee, or at least a fee structure. The fee structure can be as creative as the engaged parties wish, but in fact tend to fit a few common models. A couple of examples are:

@@

In this way, Bayesian Networks reduce computations required to find the probability of a unique combination given other explanatory variable values, while still taking into account many conditional dependencies that Naive Bayes, for example, cannot [@Barber2012]. Also, some equations for a combination are now clones of another combination and do not require recalculation. Calculating the conditional probability tables for each variable is still much more computationally expensive than Naive Bayes (as Naive Bayes is the simplest form of a Bayesian Network) and variables with many categories dramatically increases the expense [@Zhang2004].

@@

Only three of the model blending techniques used the 8 variables determined above. These were FWLS, Random Forest, and Boosted Trees. The remaining 3 techniques used only the predictions of the three individual models. All six methods were compared against the original Logistic Regression model. Initially 100 train/test runs were performed for each blending method by running 20 iterations of 5-fold cross validation. The AUC results of these iterations are displayed below:

@@

This chapter first presents the full range of method results in terms of improvements to the case study's bottom line. A business decision making scenario was created so that profit curves based on the decision rule could be built and analysed. From the profit curves, optimal probability thresholds could be derived for each method (individual and blended methods). These threshold points allowed the probability output from each model to be converted to categorical output (profit or loss), which in turn could generate confusion matrix statistics for each method. The confusion matrix statistics are discussed after the profit curve results and discussion. Then, output from the method which produced the best profit curve was used to create two subsets of profitable and loss mkaing projects. The characteristics of these subsets are compared and contrasted to gauge any overall trends. Finally, alternate ways of framing the business decision scenario are proposed.

@@

The plot below illustrates the distrubtion of profit curves for each method, where the solid lines join the mean values at each threshold point. The grey ribbon illustrates the 95% confidence interval for the profit improvement ratio at each threshold point for the 100 models.

```{r profit_curve, fig.height = 6, fig.cap = c("Profit Curves summarising results from 100 models of 9 methods: 3 simple blends, 3 complex blends, and the original 3 best methods.")}

@@

Secondly, the nearest neighbour algorithm is automatically run with the predictive model and its results are displayed in the second main tab. The aim was to provide the user with a cross check of the algorithm's results by finding projects with the most similar features to the one currently being assessed. This triggers memories from the user's past experiences on similar projects and promotes communication with other managers who delivered the 'nearest neighbours'. Some screen shots of the nearest neigbhour graphic are presented below.

@@

The general aim was to use statistical techniques to model the profitability of projects for a case study consulting business using their internal CRM data. This was rigorously completed by approaching the prediction of 'profitability' in two ways: as a regression problem predicting the degree of profitability and as a binary classification problem predicting either profit or loss. Several statistical and machine learning approaches were applied to both problems including Naive Bayes, Bayesian Networks, Linear Regression, Random Forests, gradient Boosted Trees as well as multiple methods of blending the individual models.

@@

Lastly, hypothesis 2 proposed that the best predictive model developed from hypothesis 1 could be shown to improve the overall profitability (bottom line) of the case study business. This theory was tested on a range of predictive models because AUC scores were not directly linked to profitability once the models were applied to a business decision scenario. The models output a probability, so an optimal probability threshold needed to be found that would dictate whether a job was classified 'profitable' or 'loss making'. A range of threshold values were trialed, and a decision framework was created where if a project was scored below the threshold it was accepted while projects above the threshold were rejected. If a project was accepted, the profits and losses were summed while if a project was rejected the profits and losses were forfeited. A perfect model would reject all loss making jobs and accept all profitable jobs, thereby improving overall profits. Final results showed the simple Logistic Regression blend of the individual Logistic Regression, Random Forest and Boosted Tree models improved profits the most. The 95% confidence interval for these improvements was between `r best.fin %>% filter(method == "simp.log") %>% .$lower_bound_95CI - 100`% and `r best.fin %>% filter(method == "simp.log") %>% .$upper_bound_95CI - 100`% using a probability threshold of `r best.t` (approximately `r ((simp.l %>% filter(mean.iter>best.t) %>% nrow)/nrow(simp.l)*100) %>% round(1)`% of projects).

These results contribute significantly to the research in cost estimation in three ways: the applied methods, the decision framework, and the appeal to user trust. Ensemble tree methods and blending had been applied minimally to cost estimation to date. Past research tested regression models and to some extent Neural Networks and CBR. The advantage of ensemble tree methods is that they provide insight into the model's structure while predicting at a similar level to Neural Networks. Next, a clear framework for how a business could tangibly improve profits was developed and proven successful. Previous studies have verified predictive accuracy but stopped short of how the algorithm would affect decisions and what the measured benefits would be. Lastly, the decision framework was progressed even further into a prototype application where user trust was addressed. Previous studies had shown that despite decades of promising research in cost estimation, decision maker's still mainly use an 'inside view' during fee estimation. This was addressed by providing intuitive plots of the model structure and a parallel nearest neighbour graph of similar internal projects to provide a clear and intuitive 'outside view'. Further work is required to test user confidence in the output.

Another topic identified for future research was to test how well managers estimate project input variables. Estimation of the time span, team size, total invoiced amount, and percentage of hours completed by professionals in particular should be tested. Initial estimates of input variables could also be kept in the database for future analysis.

Overall, this work has successfully built a mathematical blend of Logistic Regression, Random Forest, and Boosted Tree models, built on a consulting company's internal project data. This blended model can predict whether a project will be profitable or not and in a reasonable business decision framework, can guide managers in rejecting financially risky projects and improving final profitability.

>>>>

Consulting businesses give expert advice to other professionals in exchange for a fee based on the amount of time their consulting staff spends on the project. The deliverable 'expert advice' is generally in the form of a document or a package of documents. A document could range from a 5-page report written by a single person to a sequence of hundreds of drawings assembled by a team of 10 over many years. Despite the range of possible deliverables, before any project commences, the client and consultant must agree on a fee, or at least a fee structure. The fee structure can be as creative as the engaged parties wish, but in fact tend to fit a few common models. Two examples are:

@@

In this way, Bayesian Networks reduce computations required to find the probability of a unique combination given other explanatory variable values, while still taking into account many conditional dependencies that Naive Bayes, for example, cannot [@Barber2012]. Also, some equations for a combination are now clones of another combination and do not require recalculation. Calculating the conditional probability tables for each variable is still much more computationally expensive than Naive Bayes (as Naive Bayes is the simplest form of a Bayesian Network) and variables with many categories dramatically increase the expense [@Zhang2004].

@@

Only three of the model blending techniques used the 6 variables determined above. These were FWLS, Random Forest, and Boosted Trees. The remaining 3 techniques used only the predictions of the three individual models. All six methods were compared against the original Logistic Regression model. Initially 100 train/test runs were performed for each blending method by running 20 iterations of 5-fold cross validation. Summaries of a single example model from each of the blending methods can be found in the Appendix, section 11.3. The AUC results of the 100 iterations are displayed below:

@@

This chapter first presents the full range of method results in terms of improvements to the case study's bottom line. A business decision making scenario was created so that profit curves based on the decision rule could be built and analysed. From the profit curves, optimal probability thresholds could be derived for each method (individual and blended methods). These threshold points allowed the probability output from each model to be converted to categorical output (profit or loss) which in turn could generate confusion matrix statistics for each method. The confusion matrix statistics are discussed after the profit curve results and discussion. Then, output from the method which produced the best profit curve was used to create two subsets of profitable and loss making projects. The characteristics of these subsets are compared and contrasted to gauge any overall trends. Finally, alternate ways of framing the business decision scenario are proposed.

@@

The plot below illustrates the distribution of profit curves for each method, where the solid lines join the mean values at each threshold point. The grey ribbon illustrates the 95% confidence interval for the profit improvement ratio at each threshold point for the 100 models.

```{r profit_curve, fig.height = 6, fig.cap = c("Profit curves summarising results from 100 models of 9 methods: 3 simple blends, 3 complex blends, and the original 3 best methods.")}

@@

Secondly, the Nearest Neighbour algorithm is automatically run with the predictive model and its results are displayed in the second main tab. The aim was to provide the user with a cross check of the algorithm's results by finding projects with the most similar features to the one currently being assessed. This triggers memories from the user's past experiences on similar projects and promotes communication with other managers who delivered the 'Nearest Neighbours'. Some screen shots of the nearest neigbhour graphic are presented below.

@@

The general aim was to use statistical techniques to predict the profitability of projects for a case study consulting business using their internal CRM data. This was rigorously completed by approaching the prediction of 'profitability' in two ways: as a regression problem predicting the degree of profitability and as a binary classification problem predicting either profit or loss. Several statistical and machine learning approaches were applied to both problems including Naive Bayes, Bayesian Networks, Linear Regression, Random Forests, gradient Boosted Trees as well as multiple methods of blending the individual models' output.

@@

Lastly, hypothesis 2 proposed that predictive models developed from hypothesis 1 could be shown to improve the overall profitability (bottom line) of the case study business. A range of probability threshold values were trialed for each method using a decision framework where projects scored below the threshold were accepted, while projects above the threshold were rejected. If a project was rejected, the profits and losses were forfeited, and the remaining accepted profits and losses were summed. Final results showed the simple Logistic Regression blend of the individual Logistic Regression, Random Forest and Boosted Tree models improved profits the most. The 95% confidence interval for these improvements was between `r best.fin %>% filter(method == "simp.log") %>% .$lower_bound_95CI - 100`% and `r best.fin %>% filter(method == "simp.log") %>% .$upper_bound_95CI - 100`% using a probability threshold of `r best.t` (approximately `r ((simp.l %>% filter(mean.iter>best.t) %>% nrow)/nrow(simp.l)*100) %>% round(1)`% of projects).

These results contribute significantly to the research in cost estimation in three ways: the applied methods, the decision framework, and the appeal to user trust. Ensemble tree methods and blending had been applied minimally to cost estimation previously, even though ensemble trees provide insight into model structure while predicting at a similar level to Neural Networks. Next, previous studies have verified predictive accuracy but stopped short of how the algorithm would affect decisions and what the measured benefits would be. This study presented a clear framework for how a business could improve profits by applying the algorithm. Lastly, a prototype application was developed where insight into the model structure encouraged user trust  and a Nearest Neighbour chart presented an ‘outside view’ based on the company’s projects. Past surveys have reported that despite decades of promising research in cost estimation, decision maker's still mainly use an 'inside view' during fee estimation. Further work is required to test user confidence in the output.

Another topic identified for future research was to test how well managers estimate some numeric project input variables. In particular, time span, team size, total invoiced amount, and percentage of hours completed by professionals should be tested as these variables were calculated post project completion. Time span and total invoiced amount were discretised into wide categories, which should be easier for a manager to choose between.

Overall, this work has successfully built a mathematical blend of Logistic Regression, Random Forests, and Boosted Tree models, from a consulting company's internal project data. This blended model can predict whether a project will be profitable or not and in a reasonable decision framework, can guide managers in rejecting financially risky projects and improving profitability of the business.

# Appendix

Example results from a single model from each method. This is broken into the three main types of methods that were trialled:

1. Regression models
2. Classification models
3. Blended classification models

## Regression models

ANOVA Linear Regression and Random Forests were applied to profitability as a regression problem.

### ANOVA regression

Example summary of model built with core variables only:
```{r}

all8a = read.csv("all8a.csv")[,-1]

#function below outputs summary of model
final.output<- function(df=all8a, no.tests = 50, core = TRUE) {

        summary.tests = matrix(NA, nrow = no.tests, ncol = 3)

        for(i in 1:no.tests){

        if(core == FALSE){
        samp = sample.int(nrow(df), 1)                        
        #create sample df - use all variables that are complete from a sample row of data
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','return.pdol',
                                  'code.client', 'code.contact')]
        variables = vars
        } else{
                variables = c('inv.mlsto.log', 'Discipline', 'timespan.cbrt',
                              'no.users', 'pc.pro', 'Business')
        }

        #make reduced dataset with complete cases for all variables we want to use
        reduced = df[complete.cases(df[,variables]),]

        formula = paste("return.pdol ~ ")

        for(j in 1:length(variables)){
                formula = paste(formula, variables[j], sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'pc.pro' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*pc.pro', sep= " + ")
        }

        if('inv.mlsto.log' %in% variables &
           'code.client' %in% variables){
                formula = paste(formula, 'inv.mlsto.log*code.client', sep= " + ")
        }

        if('JD.Second' %in% variables &
           'no.users' %in% variables){
                formula = paste(formula, 'JD.Second*no.users', sep= " + ")
        }

        samp_size = floor(0.75*nrow(reduced))
        create.train = base::sample.int(nrow(reduced), samp_size)
        train.df = reduced[create.train,]
        test.df = reduced[-create.train,]

        cats = c('code.client', 'code.contact', 'JD.Second', 'Business', 'majority.pos')
        for(k in seq_along(cats)){
                if(cats[k] %in% variables){
                test.df = test.df[test.df[,cats[k]] %in% unique(train.df[,cats[k]]),]
        }
        }

        final = aov(as.formula(formula), data = train.df)

        fit= summary(final)

        return(fit)
}

final.output(df=all8a, no.tests = 1, core = TRUE)

Example summary of model built with all variables. Note that each model used a subset of all variables based on the available variables for a randomly selected project:

final.output(df=all8a, no.tests = 1, core = FALSE)

### Random Forest

Example summary of model built with core variables only:

final.rf.output<- function(df=all8a, no.tests = 50, core = TRUE) {

        summary.tests = matrix(NA, nrow = no.tests, ncol = 3)

        for(i in 1:no.tests){

        if(core == FALSE){
        samp = sample.int(nrow(df), 1)                        
        #create sample df - use all variables that are complete from a sample row of data
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','return.pdol')]
        variables = vars
        } else{
                variables = c('inv.mlsto.log', 'Discipline', 'timespan.cbrt',
                              'no.users', 'pc.pro', 'Business')
        }

        #make reduced dataset with complete cases for all variables we want to use
        reduced = df[complete.cases(df[,variables]),]

        if('code.client' %in% variables){
        sample = factor(sample(unique(reduced$code.client),size=53,
                                     replace=FALSE))
        reduced= reduced[reduced$code.client %in% sample,]

        reduced$code.client= factor(reduced$code.client)
        }

        if('code.contact' %in% variables){
        sample1 = factor(sample(unique(reduced$code.contact),size=53,
                                     replace=FALSE))
        reduced= reduced[reduced$code.contact %in% sample1,]

        reduced$code.contact= factor(reduced$code.contact)
        }

        formula = paste("return.pdol ~ ")

        for(j in 1:length(variables)){
                formula = paste(formula, variables[j], sep= " + ")
        }

        samp_size = floor(0.75*nrow(reduced))
        create.train = base::sample.int(nrow(reduced), samp_size)
        train.df = reduced[create.train,]
        test.df = reduced[-create.train,]

        cats = c('code.client', 'code.contact', 'JD.Second', 'Business', 'majority.pos')
        for(k in seq_along(cats)){
                if(cats[k] %in% variables){
                test.df = test.df[test.df[,cats[k]] %in% unique(train.df[,cats[k]]),]
        }
        }

        final = randomForest(as.formula(formula), data= train.df, mtry=5,ntree=500, importance=FALSE)

        }
        return(final)
}

rf.core <- final.rf.output(df=all8a, no.tests = 1, core = TRUE)

print(rf.core)
getTree(rf.core, 1) %>% head(20)
```

All variables:

```{r}
rf.all <- final.rf.output(df=all8a, no.tests = 1, core = FALSE)

print(rf.all)
getTree(rf.all, 1) %>% head(20)

## Classification models

Logistic Regression, Random Forests, Boosted Trees, Naïve Bayes, and Bayesian Networks were applied to profitability prediction as a classification problem (will a project be profitable or not?)

Example summary output imputed data:

# load imputed data
all10mice_f = read.csv("all10mice_May16.csv")[,-1]

#function for running models
test.roc <- function(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "log",
                     extra.var = NULL, mult = 1, x.folds = 10){

        auc<- rep(list(rep(0, length(dfs))), length(dfs))
        colours <- topo.colors(x.folds*mult)

        for(i in 1:length(dfs)){
                df = get(dfs[i])

                # mlsto is spinning errors, get rid of
                df = df[, !(names(df) %in% 'mlsto')]
                set.seed(seed)

                # create f.rpdol
                df$f.rpdol <- as.factor(df$b.rpdol)
                levels(df$f.rpdol)[levels(df$f.rpdol) == "0"] <- "profit"
                levels(df$f.rpdol)[levels(df$f.rpdol) == "1"] <- "loss"

                #set up 10 fold cv using caret function
                folds <- createFolds(df$f.rpdol, k = x.folds, list = T, returnTrain = F)
                #now have folds[[1]] through folds[[10]] list of rows to exclude

                #for Appendix just want one fold
                folds <- folds[[1]]

                if(mult > 1){
                        for(k in 2:mult){
                                set.seed(sample(1:1000,1))
                                folds.temp = createFolds(df$f.rpdol, k = x.folds, list = T, returnTrain = F)
                                folds = append(folds, folds.temp)
                        }
                }

                #if extra.var not found in names(df), change to NULL
                if(!is.null(extra.var)){
                        if(!(extra.var %in% names(df))) extra.var = NULL
                }

                #define formula for algorith methods, either rf, log, boost

                if(nrow(df) == 2364){
                        if(is.null(extra.var)){
                                formula <-"f.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + b.inv.log + client.totinv.log + Business + majority.pos + pc.majpos.log + JD.Second + Billing.Type"

                        }}

                if(method %in% 'boost') {
                        #no JD.Second
                        formula <-"b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + b.inv.log + client.totinv.log + Business + majority.pos + pc.majpos.log"

                if(method %in% 'naiive') {
                        formula<- "b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + inv.mlsto.log + client.totinv.log + Business + majority.pos + JD.Second + pc.majpos.log + Billing.Type + JD.Second"

                        #turn predictors and response into 'ordered' variables for roc() to work
                        test<- df[folds,]
                        levels(test$f.rpdol) <- c('profit', 'loss')
                        test$f.rpdol <- ordered(test$f.rpdol)

                        if(method %in% 'rf'){
                                fit <- randomForest(as.formula(formula), data = df[-folds,], 
                                            mtry = mtrys[i], ntree = 1000)
                                pred <- predict(fit, test, type = "prob")
                                pred <- pred[,2]

                        if(method %in% 'log'){
                                fit<- glm(as.formula(formula), 
                                          data = df[-folds,], family = binomial())
                                pred <- predict(fit, test,
                                                type = "response")
                        } 
                        if(method %in% 'boost'){
                                fit <- gbm(as.formula(formula), data = df[-folds,],
                                           distribution = "bernoulli", n.trees = 10000,
                                           shrinkage = 0.001, interaction.depth = 5,
                                           n.minobsinnode = 20)

                                pred <- predict(fit, test, n.tree = 10000, type = "response")
                        }

                        if(method %in% 'naiive'){
                                fit<- naiveBayes( as.formula(formula), df[-folds,])
                                pred <- predict(fit, test, type = 'raw')
                                pred<- pred[,2]
                        }

                        #pROC
                        pred.p <- pROC::roc(test$f.rpdol, pred)

                        if (i == 1) {
                        plot.roc(pred.p, col = colours[i], print.thres = F)

                        } else{
                        plot.roc(
                        pred.p, col = colours, add = TRUE , print.thres = F)
                        }

                        auc<- auc(pred.p)
                        names(auc) = method

        assign("auc.func", auc, envir = .GlobalEnv)
        assign("formula", formula, envir = .GlobalEnv)
        return(fit)

Log.Reg <- test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "log",
                     extra.var = NULL, mult = 1, x.folds = 10)
auc.func

summary(Log.Reg)

### Random Forest

Rand.F <- test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "rf",
                     extra.var = NULL, mult = 1, x.folds = 10)
auc.func

Rand.F
summary(Rand.F)

### Boosted Trees

Boost.T <- test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "boost",
                     extra.var = NULL, mult = 1, x.folds = 10)
auc.func

# Summary of the first tree in the boosted tree
pretty.gbm.tree(Boost.T) %>% kable

summary(Boost.T)

Naive <- test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "naiive",
                     extra.var = NULL, mult = 1, x.folds = 10)
auc.func

Naive

### Bayesian Network

[@Genie]

6 different methods for blending were applied. Three were simple and 3 were complex as listed below:
Simple:

* Averaging
* Logistic Regression
* Boosted Trees

Complex:

* Logistic Regression
* Boosted Trees 
* Random Forests

### Simple Average

if(.Platform$OS.type == 'windows'){

        source("C:/Users/n9232371/Documents/github/consult/functions.R")
} else{

        source("/Users/yam/Documents/github/consult/functions.R")

df.blend <- readRDS("dfblend.rds")

iter.auc <- function(mult =1, x.folds.iter = 5, 
                     methods = c("simp.log"),
                     df.iter = df.blend) {

        #create test and train set: 0.75/0.25
        pred.list <- vector(mode = "list", length = length(methods))
        names(pred.list) = methods

        #create model averaged column
        if("average" %in% methods){
        df.iter = mutate(df.iter, model.av = (log + rf + boost)/3) 
        }

        #set up 10 fold cv using caret function
        folds <- createFolds(df.iter$f.rpdol, k = x.folds.iter, list = T, returnTrain = F)
        #now have folds[[1]] through folds[[10]] list of rows to exclude
        folds <- folds[[1]]

                train = df.iter[-folds,]
                test = df.iter[folds,]

                if ("simp.log" %in% methods) {
                        print("simp.log")
                        fit <- glm(f.rpdol ~ norm.log + norm.rf + norm.boost,
                                   data = train,
                                   family = binomial())

                        pred <- predict(fit, test, type = "response")
                        pred.list[["simp.log"]] = rbind(pred.list[["simp.log"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

                if ("simp.boost" %in% methods) {
                        print("simp.boost")
                        fit <- gbm(b.rpdol ~ norm.log + norm.rf + norm.boost, data = train,
                                   distribution = "bernoulli", n.trees = 6000,
                                   shrinkage = 0.0005, interaction.depth = 6,
                                   n.minobsinnode = 10)

                        pred <- predict(fit, test, n.tree = 6000, type = "response")
                        pred.list[["simp.boost"]] = rbind(pred.list[["simp.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

                if ("orig.log" %in% methods) { 
                        print("orig.log")
                        pred <- test$log
                        pred.list[["orig.log"]] = rbind(pred.list[["orig.log"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

                if ("orig.rf" %in% methods) { 
                        print("orig.rf")
                        pred <- test$rf
                        pred.list[["orig.rf"]] = rbind(pred.list[["orig.rf"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

                if ("orig.boost" %in% methods) { 
                        print("orig.boost")
                        pred <- test$boost
                        pred.list[["orig.boost"]] = rbind(pred.list[["orig.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))

                if ("average" %in% methods) {
                        print("average")
                        pred <- test$model.av
                        pred.list[["average"]] = rbind(pred.list[["average"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

                if ("FWLS" %in% methods) {
                        print("FWLS")
                        fit <- glm(f.rpdol ~ norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + b.inv.log*norm.log + b.inv.log*norm.rf + Business*norm.boost + JD.Second + no.users,
                                   data = train,
                                   family = binomial())
                        pred <- predict(fit, test, type = "response")
                        pred.list[["FWLS"]] = rbind(pred.list[["FWLS"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

                if ("comp.boost" %in% methods) {
                        print("comp.boost")
                        fit <- gbm(b.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost, 
                                   data = train,
                                   distribution = "bernoulli", n.trees = 6000,
                                   shrinkage = 0.0005, interaction.depth = 3,
                                   n.minobsinnode = 10)

                        pred <- predict(fit, test, n.tree = 6000, type = "response")
                        pred.list[["comp.boost"]] = rbind(pred.list[["comp.boost"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

                if ("comp.rf" %in% methods) {
                        print("comp.rf")
                        fit <- randomForest(f.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost,
                                            data = train, mtry = 3, 
                                            ntree = 1000, importance = TRUE
                        )
                        pred <- predict(fit, test, type = "prob")
                        pred <- pred[, 2]
                        pred.list[["comp.rf"]] = rbind(pred.list[["comp.rf"]],
                                                        data.frame("index" = folds,
                                                                   "pred" = pred,
                                                                   "iteration" = paste("iter",ceiling(x.folds.iter), sep = "")))
                }

        #pROC
                        pred.p <- pROC::roc(test$f.rpdol, pred)

                        plot.roc(pred.p, col = "darkblue", print.thres = F)

                        auc<- auc(pred.p)  
                        assign("auc.func", auc, envir = .GlobalEnv)

        return(fit)

simp.av <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("average"),
                     df.iter = df.blend)
auc.func

#### Simple Blend

simp.LR <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("simp.log"),
                     df.iter = df.blend)
auc.func
summary(simp.LR)

#### Complex Logistic Regression Blend

```{r}
complex.LR <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("FWLS"),
                     df.iter = df.blend)
auc.func
summary(complex.LR)

### Boosted Trees

#### Simple Blend

```{r}
simp.boost <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("simp.boost"),
                     df.iter = df.blend)
auc.func
summary(simp.boost)

# Summary of the first tree in the boosted tree
pretty.gbm.tree(simp.boost) %>% kable

#### Complex Blend

```{r}
comp.boost <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("comp.boost"),
                     df.iter = df.blend)
auc.func
summary(comp.boost)

# Summary of the first tree in the boosted tree
pretty.gbm.tree(simp.boost) %>% kable

### Random Forest Complex Blend

```{r}
comp.rf <- iter.auc(mult =1, x.folds.iter = 5, 
                     methods = c("comp.rf"),
                     df.iter = df.blend)
auc.func
comp.rf
summary(comp.rf)
